Lab2

### 2021-07-29 src/data/DataCleaning.Rmd
udpated covid-19 data source. fixed covid-19 filter.

```{r import libraries, echo=FALSE, warning=FALSE}
library(tidyverse)
library(anytime)
# source(local=TRUE, file="../util.R")
```

```{r read in data, echo=FALSE}

d_covid <- read.csv(file = './../../data/raw/covid-counties.csv')
d_openings <- read.csv(file = './../../data/raw/COVID-19 US state policy database (CUSP) - Closures & Reopening.csv')
d_trips <- read.csv(file = './../../data/raw/Trips_by_Distance_-_2020.csv')

@@

```{r clean covid data, echo=FALSE}
# state(s) under investigation
state_id = c("OH","Ohio",39)

# dates under investigation
start_date = "2020-04-01"
end_date = "2020-04-30"

# COVID-19 data
# filters by date/state
d_covid <- d_covid %>%
  filter(d_covid, 
         date >= start_date, date <= end_date,
         grepl(paste(state_id, collapse = "|"), state)
         )

>>>>

```{r import libraries, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(anytime)
# source(local=TRUE, file="../util.R")
```

```{r read in data, echo=FALSE}
d_covid <- read.csv(url('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties-recent.csv'))
d_openings <- read.csv(file = './../../data/raw/COVID-19 US state policy database (CUSP) - Closures & Reopening.csv')
d_trips <- read.csv(file = './../../data/raw/Trips_by_Distance_-_2020.csv')

@@

```{r filter parameters, echo=FALSE}
# state(s) under investigation
state_id = c("OH","Ohio",39)

# dates under investigation
start_date = as.Date("2021-06-01")
end_date = as.Date("2021-06-30")
```

```{r clean covid data, echo=FALSE}
# COVID-19 data
# filters by date/state
d_covid <- d_covid %>%
  mutate(
    date = as.Date(date)
  ) %>%
  filter(
    date >= start_date, date <= end_date,
    grepl(paste(state_id, collapse = "|"), state)
  )
